Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
Defined abstain

A property of interest similar to the mode is the $\abstain{\alpha}$ property, in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

>>>>

A property of interest similar to the mode is the $\abstain{\alpha}$ property.
In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.

The finite loss eliciting $\alpha$ can be written $\ell(r,y) = \begin{cases}
0 & r = y\\
\alpha & r = \text{abstain}\\
1 & r \neq y, r \neq \text{abstain}\\
\end{cases}$.

\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
